---
title: "R Notebook"
output: html_notebook
editor_options:
  chunk_output_type: inline
---

# Install packages (only need once)
```{r}
# install.packages ("tidyverse", dependencies = TRUE)
# install.packages("ggthemes", dependencies = TRUE)
```

# Import/Load packages 
```{r}
library(tidyverse)
library(ggthemes)
```
# Import data
```{r}
exp1 = read_csv("exp1.csv")
# exp1 is a dataframe format 
nrow(exp1)
ncol(exp1)

colnames(exp1)
hist(exp1$rt)
```

# tidyverse verbs

```{r}
condition_data = exp1 %>% 
  select(subject, rt, typeoftrial, trialcondition, correct) %>%
  group_by(trialcondition) %>% # split mean rt across conditions
  filter(typeoftrial == "picture" &
    trialcondition %in% # only filter pictures with the following trial condition
    c("Heavy_Normal", "Light_Smashed", "Heavy_Smashed", "Light_Normal")) # c() is list 

means = condition_data %>%
  summarise(mean_rt = mean(rt), sd_rt = sd(rt), mean_acc = mean(correct)) 
  # method calls stored in new columns


```
```{r}
# matplotlib moment omg
condition_data %>%
filter(rt < 25000) %>% # control for outliers 
  # everything after ggplot is a single weirdly formatted function call 
ggplot(aes(x = rt)) +
geom_histogram(binwidth = 1000,
fill = "red", color = "black",
position = "identity")+
theme_few()+ # theme for pretty clear plot
xlab("RT (in milliseconds)") +
ylab ("Count")+
ggtitle("Histogram of RT")

# Plot of mean reaction time
means %>%
ggplot(aes(x = trialcondition, y = mean_rt)) +
geom_bar(stat = "identity", fill="magenta")+
theme_fivethirtyeight()+
xlab("RT (in milliseconds)") +
ylab ("Count")+
ggtitle("Barplot of RT")
```

# practice verbiage
```{r}
# exp1 %>% # not stored in a var
#   select(dataset, correct, typeoftrial) %>%
#   filter(correct == 1 & typeoftrial == "picture")


```
# QUICKSTART: Basic pipeline for analyses
- Install packages once with install.packages("name"). Check if packages are installed by typing its name into the console, eg library(stats)
    Tidyverse is a collection of other packages (ggplot1, dplyr)
- Load all packages with library(name)
- Read the csv with read_csv(String name)
- Save csv in the current directory with write_csv(data_frame, String filename)

SYNTAX FUNCTIONS AND OPERATIONS
- exp1 %>% operation %>%
- item %in% c(element 1, element 2, element 3)
- filter(field == something) for rows and select(field) for columns


# Experiment 2
```{r}
df = read_csv("relatedness_exp.csv") # df is shorthand for data frame 

# Creating a subset of df 
part_df = exp2 %>% 
  select(ID, Type, pathlength, RT) %>%
  filter(Type == "Related" & (pathlength == 1 | pathlength == 2))

# Create 3 data frames

# The mean RT for the full dataset
mean_all = df %>% 
  summarize(mean = mean(RT))
# The mean RT for the truncated dataset
mean_part = part_df %>% 
  summarize(mean = mean(RT))
# Mean RT for each subject 
mean_ID = df %>% 
  group_by(ID) %>%
  summarize(mean = mean(RT))

# print("mean RT rows: ", nrow(mean_all) )
```

